Supplementary Material

### 2025-08-04 supplementary-materials.Rmd
Update additional documents

---
## Rscript -e "rmarkdown::render('supplementary-materials.Rmd')"
## libreoffice --headless --convert-to pdf supplementary-materials.docx
title: Supplementary Material
subtitle:"Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study in India"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
      toc: true
---

@@

| Cluster                                                       | City       | Beds | Type    |
+---------------------------------------------------------------+------------+------+---------+
| Dr R N Cooper Municipal General Hospital                      | Mumbai     | 600  | Public  |
| Seth GS Medical College and KEM Hospital                      | Mumbai     | 1800 | Public  |
| Lokmanya Tilak Municipal Medical College and General Hospital | Mumbai     | 1850 | Public  |
| MEDICA Superspeciality Hospital                               | Kolkata    | 300  | Private |
| Medical College                                               | Kolkata    | ??   | Public  |
| Nilratan Sircar Medical College & Hospital                    | Kolkata    | 1910 | Public  |
| Postgraduate Institute of Medical Education and Research      | Chandigarh | 1400 | Public  |
+---------------------------------------------------------------+------------+------+---------+

>>>>

---
## Rscript -e "rmarkdown::render('supplementary-materials.Rmd')"
## libreoffice --headless --convert-to pdf supplementary-materials.docx
title: Supplementary Material
subtitle:"Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study in India"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
      toc: true
      toc_depth: 1
---

@@

| Cluster | City | Beds | Type |
|---------|------|------|------|
| Dr R N Cooper Municipal General Hospital | Mumbai | 600 | Public |
| Seth GS Medical College and KEM Hospital | Mumbai | 1800 | Public |
| Lokmanya Tilak Municipal Medical College and General Hospital | Mumbai | 1850 | Public |
| MEDICA Superspeciality Hospital | Kolkata | 300 | Private |
| Medical College | Kolkata | 2140 | Public |
| Nilratan Sircar Medical College & Hospital | Kolkata | 1910 | Public |
| Postgraduate Institute of Medical Education and Research | Chandigarh | 1400 | Public |
